---
title: "Ames_Project"
author: "Braden Anderson and Rayon Morris"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

source("./Functions.R")
```


```{r}
df <- read.csv("./train.csv")
head(df)

```
```{r}

# Convert the Neighborhood column to a factor, so it is compatible with creating
# linear models with lm.
df[,"Neighborhood"] <- factor(df[,"Neighborhood"])

# Set the desired reference level within the neighborhood factor.
df <- within(df, Neighborhood <- relevel(Neighborhood, ref="NAmes"))

```


```{r}

# Filter dataframe such that it only includes rows where the neighborhood column
# is one of the neighborhoods we are interested in for the part 1 analysis.

# Neighborhoods that Century 21 Ames real estate sells in
interesting_neighborhoods <- c("NAmes", "Edwards", "BrkSide")

# Create a new dataframe that only contains the neighborhoods Centry 21 Ames sells in
century_df <- df[(df[,"Neighborhood"] %in% interesting_neighborhoods), ]
century_df[,"Neighborhood"] <- droplevels(century_df[,"Neighborhood"])

# Verify the new dataframe only contains the neighborhoods: NAmes, Edwards, and BrkSide
unique(century_df[,"Neighborhood"])
levels(century_df[,"Neighborhood"])
```

```{r}

# NOTES AND PART 1 OUTLINE:

# Three potential regression models for SalePrice on GriLivArea across three neighborhoods of interest:
#
# 1) Equal Lines Model <-- Single regression line for all neighborhoods. The estimated mean house price for a given
#                          house size is exactly the same, no matter which neighborhood the house is in.   
#
# 2) Parallel lines model <-- The rate of change in the mean house price, associated with a 1 unit increase in square
#                             footage is the same for each neighborhood. Additionally, the difference in intercepts
#                             represents the constant difference in mean house prices between neighborhoods, across all values
#                             of the explanatory variable (house size).
# 
# 3) Separate lines model <-- The rate of change in mean house price, associated with a 1 unit increase in square footage
#                             is different depending on which neighborhood the house is in.
#
#
# Statistical sleuth page 250: When to Include Interaction Terms
# 1) When a question of interest pertains to interaction (meadowfoam study).
# 2) When good reason exists to suspect interaction.
# 3) When interactions are proposed as a more general model for the purpose of examining
#    the goodness of fit for a model without interaction.


# ********** Questions of interest **********
# 1) How does the SalePrice of a house relate to the square footage of the house (GrLivArea)?
# 2) Does the relationship between SalePrice and square footage depend on what neighborhood the house is located in?


# STRATEGY FOR QUESTION OF INTEREST #2:
#
#
# Step 1: Start with the fullest model (separate lines model)
#
# Step 2: Examine the residual plots for the separate lines model to check if the
#         assumptions for an F-test are met. 
#
# Step 3: If assumptions are met, perform a partial F-test for the hypothesis that
#         the interaction terms can be dropped. (i.e. extra sum of squares test where the separate 
#         lines model is the full model and the parallel lines model is the reduced model. This checks 
#         if we can reduce down to using the parallel lines model instead). A high p-value indicates that
#         the parallel lines model is adequate.
#
# NOTE: Step 3 essentially asks the question, does the relationship between SalePrice and house
#       size change based on what neighborhood you are in? If the p-value is high, the slopes can be 
#       the same (parallel lines), and the answer can be: No, the relationship does not change
#       based on neighborhood. If the slopes cannot be the same, the relationship does change based
#       on neighborhood.
#
# Step 4: If Step 3 showed that the interaction terms can be dropped, we may want to perform
#         another partial F-test for the hypothesis that the intercepts in the parallel lines
#         models are the same (i.e. full model=parallel lines, reduced model=equal lines).
#
# NOTE: Step 4 does not have an entirely logical interpretation in the context of the problem, 
#       because it essentially asks "Does the SalePrice of a house with a square footage of zero
#       change based on what neighborhood you're in?". (A more useful interpretation may be, does the
#       minimum house price change based on what neighborhood you're in, however interpreting this way
#       seems shakey because that is not really what the intercept represents). It must also be noted
#       that attempting to interpret the intercept here is dangerous to begin with, as the minimum
#       house size in the entire data set is 334 square feet, therefore statements made about houses
#       with square footage below this value requires extrapolation, and are therefore dangerous and unlikely
#       to be useful.

```

#Model 1: Separate Lines Model
```{r}

separate_fits <- lm(SalePrice~GrLivArea+
                      Neighborhood+             # Add intercept adjustment terms
                      Neighborhood:GrLivArea,   # Add interaction terms (slope adjustments)
                    data=century_df)


summary(separate_fits)
```

```{r}

# PLOT THE SEPARATE LINES MODEL
plot_slr_via_mlr(fit=separate_fits, 
                 df=century_df,
                 model_type="separate_lines",
                 explanatory_continuous="GrLivArea", 
                 explantory_grouping="Neighborhood",
                 response="SalePrice",
                 alpha=0.5,
                 plot_group_means=TRUE,
                 identify_obs=c(524, 1299, 643, 725))

```


# Assessing Regression Assumptions for the Separate Lines Model

## Linearity Assumption: Separate Lines Model
```{r}

plot_residuals(separate_fits, 
               dataframe=century_df,
               residual_type="externally_studentized", 
               plot_zero_hline=TRUE, 
               extreme_thresh_regular=5, 
               flag_extreme_values=TRUE, 
               id_extreme_values=TRUE)

# The majority of the residual plot is a reasonable representation of the ideal "random cloud", providing evidence
# that the linearity assumption is met for most of the data. We should note observations 1299, 643, 1424, and 725 do have
# rather large residual values that may be worth investigating. 

```

# Indepdence Assumption: Separate Lines Model
```{r}

# From the residual plot above, do not see any "tracking" in the residuals. Based on how the data was collected
# we do not have a reason to suspect that serial or cluster effects exist. The Independence assumption is always
# difficult to be completely confident in without intimate knowledge of the data collection process, however
# we will proceed with caution as if this assumption is met.

```


# Normality Assumption: Separate Lines Model
```{r}

plot_residual_qq(fit=separate_fits,
                 dataframe=century_df,
                 residual_type = "externally_studentized")


# Based on the QQPlot of the externally studentized residuals shown below, we see that overall the quantiles of 
# the residuals are linearly related to the theoretical quantiles of the normal distribution. That said, we again 
# note that there are still the same few observations raising concern in terms of evidence against the normality
# assumption (specifically: observations 725, 643, and 1299).
#
# An "S" shape in a residual QQPlot indicates that one of the distributions (the observed or theoretical), has  
# longer tails than the other. In this QQplot we see the observations mentioned above (725, 643, 1299) forming
# this characteristic "S" shape, which means for these particular data points the normality assumption is not met.
```

```{r}

plot_residual_histogram(fit=separate_fits, 
                        dataframe=century_df,
                        residual_type="externally_studentized", 
                        overlay_normal = TRUE, 
                        num_bins=75,
                        normal_linecolor="purple")

# The residual histogram confirms what we see in the residual QQplot. This plot offers another perspective
# but tells the same story; that are a few observations causing some significant "long taildness", which violates
# the normality of errors assumption.

```



```{r}

plot_residuals(separate_fits, 
               dataframe=century_df,
               residual_type="externally_studentized", 
               plot_zero_hline=TRUE, 
               extreme_thresh_regular=5, 
               flag_extreme_values=TRUE, 
               id_extreme_values=TRUE)

# Lastly, we can review the plot of externally studentized residuals (shown two plots above, but reproduced here) 
# in the context of the normality assumption.
#
# From the residual plot we see that, for the most part, the residuals seem to be normally distributed around zero,
# and are not consistently shifted in either the positive (upward) or negative (downward) direction which would be 
# indicative of a heavily skewed distribution. This plot also helps us identify some potential outliers, 
# (observations 725, 643, 1299, 1424) that may be violating the normality assumption.

```

# Equal Variance Assumption: Separate Lines Model
```{r}

plot_residuals(separate_fits, 
               dataframe=century_df,
               residual_type="externally_studentized", 
               plot_zero_hline=TRUE, 
               extreme_thresh_regular=5, 
               flag_extreme_values=TRUE, 
               id_extreme_values=TRUE)

# Reviewing the residual plot in the context of the equal variance assumption, we do see some slight
# "fanning" or "funnel shaped" pattern in the plot, which provides evidence against equality of variance.
# Specifically, it seems that the variance may be greater for the more expensive homes.
#
# That said, the evidence against homoscedasticity is not extreme, and it seems that the 
# spread of the residuals about zero is reasonably consistent across the range of fitted values for 
# most observations (again with the exception of the same, previously mentioned, troublesome observations).
#
# In terms of a violation of equality of variance, observations 643 and 1299 are particularly concerning.
# These observations have quite large residuals, and considering that there are no other
# observations even close to these fitted values it would be rather unusual to observe such a large
# residual value there. 
#
# Imagine taking just a handful of samples from a normal distribution, and having two of those samples 
# be more than 4.5 standard deviations away from the mean. That would be cause to question whether or not 
# those draws really came from the same population as the others, which is the exact question we are faced with 
# when it comes to observations 643 and 1299. 
#
# Observation 1424 is less concerning because there are many other samples in that range of the fitted values,
# and as more samples are taken we would expect a few large residuals to occur. This is because with a larger sample
# size we expect the normal distributions (conditioned at each fixed X) to be more fully explored.
#
# Observation 725 also exists in a heavily populated area of the fitted values, however the extremely large 
# residual (more than 6 standard deviations away from the mean), still seems very unlikely to occur even if
# a moderate number of samples were taken (assuming observation 725 truly does come from a population with the
# same variance as the other samples).
#
# Summary: Observations 725, 643, and 1299 show evidence that they may come from a population with a 
#          different variance than the others, therefore these observations provide evidence against
#          the equal variance assumption. Additionally, the slight fanning shown in the plot can be 
#          interpreted as evidence against equality of variance, where there would be higher variability
#          in more expensive homes than in lower priced homes. 
```

# Check for influential observations: Separate Lines Model
```{r}
plot_residual_vs_leverage(fit=separate_fits,
                          dataframe=century_df,
                          residual_type="externally_studentized",
                          resid_line_threshold=4.5)
```

```{r}
plot_residual_vs_leverage(fit=separate_fits,
                          dataframe=century_df,
                          residual_type="externally_studentized",
                          resid_line_threshold=1.7)


# Observations 643, 524 and 1299 all have leverage values greater than 3 times the
# average leverage, as well as significantly large residuals. For observations 643 and 1299 
# the residual values are more than 4.5 standard deviations from zero, while observation
# 524 has leverage more than 1.7 standard deviations from zero.
```



```{r}

# Statistical Sleuth Section 11.3, page 345
# "Least Squares regression analysis is not resistant to outliers. One or two observations can
# strongly influence the analysis, to the point where the answers to the questions of interest 
# change when these isolated cases are excluded. Although any influential observation that comes
# from a population other than the one under investigation should be removed, removing an observation
# simply because it is influential is not justified. IN ANY CIRCUMSTANCE, IT IS UNWISE TO STATE 
# CONCLUSIONS THAT HINGE ON ONE OR TWO DATA POINTS. SUCH A STATISTICAL STUDY SHOULD BE CONSIDERED
# EXTREMELY FRAGILE. 

# FOLLOW FLOW CHART ON PAGE 321, DISPLAY 11.8.
# 1) Answer QOI #2 with all observations.
# 2) Answer QOI #2 with observations 1299 and 524 removed.
#
# If the answer to QOI #2 changes in 1) and 2) above, then:
#
# Proceed with the analysis where observations 1299 and 524 and removed, then when reporting  
# the results restrict the domain of inference to only houses that are smaller than 4000 square feet.

```


# Answer QOI #2 with all observations included.
```{r}

parallel_fits <- lm(SalePrice~GrLivArea +
                      Neighborhood,        # Add intercept adjustments (Parallel lines model)
                     data=century_df)

summary(parallel_fits)
```


```{r}

partial_f <- partial_f_test(full_model=separate_fits,
                            reduced_model=parallel_fits)

partial_f

# This shows a partial (extra sum of squares) F-test for the hypothesis that
# the interaction terms can be dropped. The very small p-value (6.148x10^-8)
# provides convincing evidence that the parallel lines model is not an adequate
# substitution for the separate lines model.
#
# In other words, the difference between the sum of squared residuals in the full
# model and the reduced model is greater than could be explained by the extra parameters
# in the full model simply modeling some chance variation in the data (statistical sleuth page 285).
#
# The fact that the interaction (slope adjustment) terms in the full model are significantly
# different from zero (32.847, p-value=0.0025, and -24.566, p-value=0.00013) are also evidence
# that agrees with this partial F-test result (i.e. that the parallel lines model is not an 
# adequate replacement for the separate lines model).
#

```


```{r}
confint(separate_fits)

# Answer to QOI #2, all observations in the dataset included:
# 
# The relationship between the SalePrice of a home and its square footage (GrLivArea) does
# depend on what neighborhood the home is in. The dependence is such that the rate of change
# of the mean home value associated with a 1 unit increase in living area is different depending
# on what neighborhood the home is located in. 
#
# Specifically:
#
# Our best estimate for the rate of change of the mean home value associated with a 1 unit
# increase in square footage, for a home in the NAmes neighborhood is $54.316. Additionally, we are
# 95% confident that the true value of this mean increase is contained within the interval ($45.24, $63.38).
#
# Our best estimate for the rate of change of the mean home value associated with a 1 unit
# increase in square footage, for a home in the BrkSide neighborhood, is $(54.316 + 32.847) = $87.163.
# Additionally, we are 95% confident that the true value of this mean increase is contained within
# the interval ($(54.316 + 11.5806), $(54.316 + 54.112)) = ($65.896, $108.428).
#
# Our best estimate for the rate of change of the mean home value associated with a 1 unit
# increase in square footage, for a home in the Edwards neighborhood, is $(54.316 - 24.566) = $29.75.
# Additionally, we are 95% confident taht the true value of this mean increase is contained within 
# the interval ($(54.316 - 37.073), $(54.316 - 12.057)) = ($17.243, $42.259).
#
#
# NAmes Neighborhood    --> Best Estimate: $54.316, 95% CI: ($45.24, $63.38)
# BrkSide Neighborhood  --> Best Estimate: $87.163, 95% CI: ($65.896, $108.428)
# Edwards Neighborhood  --> Best Estimate: $29.75,  95% CI: ($17.243, $42.259)
```

# Answer QOI #2 with observations 524 and 1299 removed
```{r}

# Create a new dataframe where observations 524 and 1299 and been removed
century_obsrm_df <- century_df[(century_df[,"Id"] != 524) & (century_df[,"Id"] != 1299),]

# Fit the separate lines model on this new dataset where 
# observations 524 and 1299 have been removed
separate_fits_obsrm <- lm(SalePrice~GrLivArea+
                            Neighborhood+             # Add intercept adjustment terms
                            Neighborhood:GrLivArea,   # Add interaction terms (slope adjustments)
                          data=century_obsrm_df)


summary(separate_fits_obsrm)
```


```{r}

# Fit the parallel lines model using the dataset where 
# observations 524 and 1299  have been removed
parallel_fits_obsrm <- lm(SalePrice~GrLivArea +
                            Neighborhood,        # Add intercept adjustments (Parallel lines model)
                     data=century_obsrm_df)

summary(parallel_fits_obsrm)
```

```{r}

# PLOT THE SEPARATE LINES MODEL FOR THE DATASET WITH 
# OBSERVATIONS 524 AND 1299 REMOVED
plot_slr_via_mlr(fit=separate_fits_obsrm, 
                 df=century_obsrm_df,
                 model_type="separate_lines",
                 explanatory_continuous="GrLivArea", 
                 explantory_grouping="Neighborhood",
                 response="SalePrice",
                 alpha=0.5,
                 plot_group_means=TRUE,
                 identify_obs=c(643, 725))

```

```{r}

partial_f_obsrm <- partial_f_test(full_model=separate_fits_obsrm,
                                  reduced_model=parallel_fits_obsrm)

partial_f_obsrm

# Although the evidence is significantly less (partial F-test p-value=0.001156 with observations
# 526 and 1299 removed, compared to partial F-test p-value=6.148x10^-8 with all observations included)
# The conclusion of the partial F-test has not changed. In other words, we still reject the hypothesis
# that the parallel lines model is an adequate replacement for the separate lines model.
#

```


```{r}
confint(separate_fits_obsrm)

# While the high level answer to the question of interest remains the same (i.e. that the relationship
# between SalePrice and the square footage of a home does depend on what neighborhood the home is in,
# and that the dependence is such that the rate of change in mean home value associated with a 1 unit
# increase in square footage is different for each neighborhood), the specific details of this answer
# have changed.
#
#
# ANSWER TO QOI #2, WHEN OBSERVATIONS 524 AND 1299 ARE NOT INCLUDED IN THE ANALYSIS:
#
# Our best estimate for the rate of change of the mean home value associated with a 1 unit
# increase in square footage, for a home in the NAmes neighborhood is $54.316. Additionally, we are
# 95% confident that the true value of this mean increase is contained within the interval ($45.79, $62.83).
#
# Our best estimate for the rate of change of the mean home value associated with a 1 unit
# increase in square footage, for a home in the BrkSide neighborhood, is $(54.316 + 32.847) = $87.163.
# Additionally, we are 95% confident that the true value of this mean increase is contained within
# the interval ($(54.316 + 12.866), $(54.316 + 52.826)) = ($67.182, $107.142).
#
# Our best estimate for the rate of change of the mean home value associated with a 1 unit
# increase in square footage, for a home in the Edwards neighborhood, is $(54.316 + 21.660) = $75.976.
# Additionally, we are 95% confident taht the true value of this mean increase is contained within 
# the interval ($(54.316 + 4.357), $(54.316 + 38.96)) = ($58.673, $93.276).
#
# ========================================================================================================
#
# SUMMARY OF DIFFERENCES IN HOW QOI #2 IS ANSWERED, WITH AND WITHOUT OBSERVATION 524, 1299 REMOVAL
#
# WITH ALL OBSERVATIONS, RATE OF CHANGE OF MEAN SALEPRICE ASSOCIATED WITH 1 UNIT INCREASE IN SQFT:
# 
# NAmes Neighborhood    --> Best Estimate: $54.316, 95% CI: ($45.24, $63.38)
# BrkSide Neighborhood  --> Best Estimate: $87.163, 95% CI: ($65.896, $108.428)
# Edwards Neighborhood  --> Best Estimate: $29.75,  95% CI: ($17.243, $42.259)
#
# WITH OBS 524 AND 1299 REMOVED, RATE OF CHANGE OF MEAN SALEPRICE ASSOCIATED WITH 1 UNIT INCREASE IN SQFT:
#
# NAmes Neighborhood    --> Best Estimate: $54.316, 95% CI: ($45.79, $62.83)
# BrkSide Neighborhood  --> Best Estimate: $87.163, 95% CI: ($67.182, $107.142)
# Edwards Neighborhood  --> Best Estimate: $75.976, 95% CI: ($58.673, $93.276)
#
# SUMMARY: The best estimates for the NAmes and BrkSide neighborhoods were unchanged, and the confidence 
#          intervals were only slightly effect, by an ammount that were surely not be of practical significance. 
#
#          The inference regarding the Edwards Neighborhood was EXTREMELY effected. The best estimate more than 
#          doubled after removal of observations 524 and 1299 (from $29.75 to $75.976). Additionally, the 95%
#          confidence limits are vastly different. The confidence intervals changed so much that the upper 
#          bound of the interval with all observations included ($42.259) is smaller than the lower bound when
#          observations 524 and 1299 are removed ($58.673). This change would absolutely be of practical significance,
#          as we see the perspective on home prices in this neighborhood has completely changed simply by removing
#          two observations. As the statistical sleuth says, "it is unwise to state statistical conclusions that hinge
#          on just a few data points." From this perspective, it seems that the analysis with observations 524 and 1299
#          must be included in the report.
#
# ========================================================================================================
```

# Metrics
```{r}

# Calculate PRESS (PREDICTION RESIDUAL SUM OF SQUARES) for the Separate Lines Model
# that contains all observations. This value is an indicator for how well the model
# should perform on new data.

sep_lines_PRESS <- ols_press(model=separate_fits)
sep_lines_PRESS

```

```{r}
# Calculate PRESS (PREDICTION RESIDUAL SUM OF SQUARES) for the Separate Lines Model
# whereobservations 524 and 1299 were removed
sep_lines_PRESS_obsrm <- ols_press(model=separate_fits_obsrm)
sep_lines_PRESS_obsrm
```

```{r}

# Adjusted R-Squared for Separate Lines Model that contains all observations
summary(separate_fits)$adj.r.squared

```

```{r}

# Adjusted R-Squared for Separate Lines Model where 
# observations 524 and 1299 were removed
summary(separate_fits_obsrm)$adj.r.squared

```



# Revisiting Assumptions on Log Transformed Data
```{r}

# Add a column for the log of SalePrice
century_df[,"log_SalePrice"] <- log(century_df[,"SalePrice"])

# SEPARATE LINES MODEL USING THE LOG OF SALEPRICE
separate_fits_log <- lm(log_SalePrice~GrLivArea+
                          Neighborhood+             # Add intercept adjustment terms
                          Neighborhood:GrLivArea,   # Add interaction terms (slope adjustments)
                          data=century_df)


summary(separate_fits_log)  
```

```{r}

parallel_fits_log <- lm(log_SalePrice~GrLivArea +
                          Neighborhood,        # Add intercept adjustments (Parallel lines model)
                     data=century_df)

summary(parallel_fits_log)

```


```{r}

partial_f_log <- partial_f_test(full_model=separate_fits_log,
                                reduced_model=parallel_fits_log)

partial_f_log

# PARTIAL F-TEST STILL REJECT PARALLEL LINES MODEL WHEN USING
# LOG OF SALE PRICE
```


```{r}

# ADD THE LOG OF SALEPRICE TO THE DATAFRAME WITH OBSERVATIONS 524 AND 1299 REMOVED
century_obsrm_df[,"log_SalePrice"] <- log(century_obsrm_df[,"SalePrice"])




# SEPARATE LINES MODEL USING THE LOG OF SALEPRICE
separate_fits_log_obsrm <- lm(log_SalePrice~GrLivArea+
                                Neighborhood+             # Add intercept adjustment terms
                                Neighborhood:GrLivArea,   # Add interaction terms (slope adjustments)
                              data=century_obsrm_df)

# PARALLEL LINES MODEL USING THE LOG OF SALEPRICE
parallel_fits_log_obsrm <- lm(log_SalePrice~GrLivArea +
                                Neighborhood,        # Add intercept adjustments (Parallel lines model)
                              data=century_obsrm_df)


partial_f_log_obsrm <- partial_f_test(full_model=separate_fits_log_obsrm,
                                      reduced_model=parallel_fits_log_obsrm)

partial_f_log_obsrm

# PARTIAL F-TEST STILL REJECT PARALLEL LINES MODEL WHEN USING
# LOG OF SALE PRICE AND OBSERVATIONS 524 AND 1299 REMOVED
```

# PART 2:
```{r}


## Project Part 2, TODO: 
# 1) Model produced using backwards selection
# 2) Model produced using forward selection
# 3) Model produced using step wise selection
# 4) Model produced using a custom method
# 5) Plots for assumption assessment and influential point investigations for each of the 4 models above.
# 6) Adjusted RSquare, CV PRESS and Kaggle Scores for the 4 models mentioned above. 


```

```{r}

plot_residuals(separate_fits, 
               dataframe=century_df,
               residual_type="externally_studentized", 
               plot_zero_hline=TRUE, 
               extreme_thresh_regular=5, 
               flag_extreme_values=TRUE, 
               id_extreme_values=TRUE, extreme_thresh_std = 2.5)


```



```{r}

plot_residuals(separate_fits_log, 
               dataframe=century_df,
               residual_type="externally_studentized", 
               plot_zero_hline=TRUE, 
               extreme_thresh_regular=5, 
               flag_extreme_values=TRUE, 
               id_extreme_values=TRUE, extreme_thresh_std = 2.5)


```